%-------------------------
% Resume in Latex
% Author : Nathan Dinh
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Nathan Dinh} \\ \vspace{7pt}
    \small 6692132635 $|$ \href{mailto:nathan.d.workplace@gmail.com}{{\underline{nathan.d.workplace@gmail.com}}} $|$ 
    \href{https://www.linkedin.com/in/dinh97/}{\underline{linkedin.com/in/dinh97}} $|$
    \href{https://github.com/nathan-dinh-dev}{\underline{github.com/nathan-dinh-dev}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {San Jose State University}{San Jose, CA}
      {Bachelor of Science in Computer Science}{Sep. 2023 -- Dec 2025}
    \resumeSubheading
      {HCMC University of Technology}{Vietnam}
      {Bachelor of Science in Electrical Engineering}{Aug. 2015 -- May 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Freelance Software Engineer}{Jan. 2025 -- Present}
      {Ha Noi Bistros}{San Jose, CA}
      \resumeItemListStart
        \resumeItem{Engineered a robust inventory management system using Next.js, AWS Rekognition for item verification, and a MySQL relational database.}
        \resumeItem{Designed and deployed a scalable waitlist system using React Native, AWS Lambda and SNS, supporting 5 restaurant locations with infrastructure prepared for multi-store expansion.}
        \resumeItem{Reduced reliance on third-party platforms and manual processes, resulting in estimated annual savings of \$65,000 in subscription and labor costs for the business owner.}
        \resumeItem{Utilized CI/CD workflows, Git, and modular architecture to ensure rapid iteration, system reliability, and long-term maintainability.}
    \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Software Development Engineer Intern}{May. 2024 -- Oct. 2024}
      {Amoeba Software}{Lakewood, CA}
      \resumeItemListStart
        \resumeItem{Developed and maintained various front-end features using Next.js, Auth0, and TypeScript.}
        \resumeItem{Implemented Redis caching to optimize search queries, reducing average response time by 20\%.}
        \resumeItem{Implemented Redux to manage state and API interactions across seven routes, ensuring smooth front-end and back-end integration.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Development Engineer Intern}{May. 2024 -- Aug. 2024}
      {Graph Academy - Remote}{Cupertino, CA}
      \resumeItemListStart
        \resumeItem{Maintained web-based platform with Next.js and TypeScript for Visual 2nd Brain project.}
        \resumeItem{Contributed to backend by integrating Supabase and a background removal API using Node.js, cutting image processing time by 30\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Face Recognition Attendance System} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{Jan. 2025 -- Present}
            \resumeItemListStart
            \resumeItem{Developed a full-stack attendance tracking system with a Flask REST API and React frontend.}
            \resumeItem{Implemented face recognition using YOLOv9, trained on custom datasets to accurately identify individuals.}
            \resumeItem{Persisted attendance data in PostgreSQL and deployed the containerized stack using Docker.}
            \resumeItem{Utilized Redis and Celery for asynchronous background tasks such as image processing and data logging.}
        \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Naptastic} $|$ \emph{Next.js, TypeScript, Clerk, Stripe, Supabase, Prisma, GitHub Actions}}{Sep. 2024 -- Jan 2025}
          \resumeItemListStart
            \resumeItem{Developed an end-to-end fullstack Airbnb-style web application with front-end design using TailwindCSS and Shadcn/UI to create responsive layout components.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Anna Kitchen} $|$ \emph{React, Stripe, OAuth2, Express, MySQL, GitHub Actions}}{Jun. 2023 -- Dec. 2023}
        \resumeItemListStart
            \resumeItem{Developed a fully functional online food ordering web application with responsive UI using Reactstrap.}
            \resumeItem{Integrated Stripe for secure payments, OAuth2 for authentication, and automated CI/CD with GitHub Actions.}
            \resumeItem{Partnered with a friend to launch the application in production, supporting food sales and generating over \$20,000 in annual revenue.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, TypeScript, Java, Python, C/C++, SQL, HTML/CSS} \\
     \textbf{Frameworks and Libraries}{: React, Redux, Flask, Zod, Next.js, Prisma, MongoDB, Strapi, Express.js, Node.js, MySQL, Redis, TailwindCSS, Shadcn/ui, Reactstrap, TanStack, FastAPI.} \\
     \textbf{Developer Tools}{: Git, Docker, Jira, Jenkins, Firebase, Supabase, Auth0, AWS, Vercel, Render} \\
    }}
 \end{itemize}

%-----------PROGRAMMING SKILLS-----------
% \section{Certificates}
% \begin{itemize}[leftmargin=0.15in, label={}]
%   \item \small{
%     MIT Professional Certificate in Coding: Full Stack Development with MERN \hfill \textit{Oct. 2023}
%   }
% \end{itemize}

%-------------------------------------------
\end{document}